Static Analysis by Path Focusing

### 2011-06-12 report/report.tex
report ~final

\acknowledgement{
	I would like to thank my two tutors, David Monniaux and Matthieu Moy, for
	their direction of my master thesis, and for their help during all my
	internship. I thank them for all their explanations that clearified lots of
	my questions, and for their advices for the redaction of this report.
}

>>>>

\acknowledgement{
	I would like to thank my two tutors, David Monniaux and Matthieu Moy, for
	their direction of my master thesis, and for their help everytime I needed
	it. I thank them for all their explanations that clearified lots of
	my questions, and for their advices for the redaction of this report.\\
	I also thank Laure Gonnord for inviting me to present my work at the GDR GPL
	2011.\\
	Finally, I thank all the Synchrone team and the Verimag laboratory for their
	cheerful welcome.
}
